---
title: "Creating an annotated map"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating an annotated map}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  echo=TRUE,
  message=FALSE,
  warning=FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

In this vignette, you will learn how to add new information to a map. Here, we retrieve a map of Manhattan, NYC. 


```{r setup}
library(cartographr)
library(ggplot2)
library(dplyr)
library(sf)
```

First, we load the locations of crimes in Manhattan. 


```{r load crime locations, echo=T, message=F}
data("crime") 
```

# Convert longitude / latitude into a `sf`

To add the crime locations in the dataset to our map, we harness the `sf` (simple features) package, which includes a lot of useful tools for working with geo data. To this end, we convert the dataset into a `sf` object using latitude and longitude.  

```{r convert to sf}
df_crime <- crime |> 
 st_as_sf(coords = c("longitude", "latitude"), crs=4326, remove = F) |>
 filter(date >= "2023-01-01" & date < "2024-01-01")

df_crime |> head()
```

This can be achieved with the function `sf::st_as_sf()` using the coordinates from the dataset. 

# Setup the map parameters

We have to provide `longitude`, `latitude` and `x_distance` (i.e., the width of the map in meters). Furthermore, we define the extend of the OSM data in meters in `get_osmdata()`. `y_distance` is calculated automatically using the output size aspect ratio. 

```{r define coordinates}
set_output_size("A3", orientation = "portrait")
osm <- get_osmdata(lat = 40.711, lon =-74.009, x_distance =  1300)
```

# Plot the map

`plot_map()` generates a `ggplot2` object using the color theme set as parameter. That means that we can easily adjust the plot using `ggplot2` commands and also add new information to the map.

```{r plot map, fig.dim=c(11.7,16.5), fig.dpi = 72, out.width="100%"}
p <- osm |> plot_map(palette = "metropolitan")  +
  # add geom with crimes
  geom_point(data = suppressMessages(sf::st_intersection(df_crime, osm$bbox |> sf::st_as_sfc())),
             aes(x = longitude, y = latitude, shape = type), color="#222424", size=2) + 
  theme_infomap_barlow() + 
  # Set labels
  labs(title = "NEW YORK CRIME (2023)",
       shape = "TYPE")

p
```

# Save map

`save_map()` can be used to store the print-ready plot object to the disk as a drawn object in `pdf` format. 

```{r save map, eval=F}
save_map(plot = p, filename = "~/ny_crime.pdf")
```
