---
title: "Creating postcards"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating postcards}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  echo=TRUE,
  message=FALSE,
  warning=FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

This vignette shows how to create postcards (or also posters, when used with larger output formats).

```{r setup}
library(cartographr)
library(ggplot2)
library(dplyr)
library(ggpubr)
library(osmdata)
```

# Setup the map parameters.

We have to provide `longitude`, `latitude`. Furthermore, we define the extend of the OSM data in meters in `get_osmdata`. Here, we will use a map width of 1200 _m_. Also, in this example we will create several instances for different maps (cities).

```{r define coordinates}
osmdata::get_overpass_url()
osmdata::set_overpass_url("https://overpass.kumi.systems/api/interpreter")

df_coords <- tibble(lat = c(53.54514883288921,47.374566535402685,48.873810503366016),
       lon = c(10.000039228206994,8.538175481044222,2.2950207999211405),
       y_distance = rep(1200*sqrt(2), 3),
       x_distance = rep(1200,3),
       name = c("hamburg","zürich","paris"),
       color = c("berlin", "imhof","macau"))

df_coords |> head()
```

Having defined our input data, we can feed it into the `get_osmdata()` function. Afterwards, we directly preprocess the maps using `preprocess_map()` and store it in a new column called `osm_pps`. 

```{r retrieve data}
df_coords <- df_coords |> 
  rowwise() |>
  # 1. retrieve osm data
  mutate(osm = list(get_osmdata(lat, lon, y_distance, x_distance) )) |>
  # 2. preprocess data
  mutate(osm_pps = list(preprocess_map(osm))) |>
  # 3. remove rowwise() grouping
  ungroup()

df_coords |> head()
```

# Plot map

Now, we create ggplot2 objects for each prepocssed `osm_pps` object. 

```{r plot map, fig.dim=c(12,5.8), fig.dpi=72}
df_coords <- df_coords |> 
  rowwise() |>
  # Create ggplot2 objects
  mutate(plot = list(
    plot_map(osm_pps, color = get_color(color), scaling = get_scaling("A6"))+
    labs(title=name)+
    theme_postcard(get_scaling("A6"))+ 
    theme(plot.background =element_rect(fill="#FFFFFE",color="#AAAAAA"))
    )
  ) |>
  ungroup()
           
ggarrange(plotlist = df_coords$plot, ncol = 3)
```

# Save map

```{r save map, eval=F}
df_coords |> 
    rowwise() |>
    mutate(res = save_map(plot = plot, filename=paste0("~/postcards/",name,"_A6_",color,".pdf")))
```
